\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-21 icse/eval.tex
Updated the number of grammars

\begin{figure}[t]
  \[
    \begin{array}{c|r|r|r|r|r|r}
      \hline
      \textbf{version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c|}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\hline
      \text{\# lexical prod.}
      & \text{\inred{XX}}
      & \text{\inred{XX}}
      & \text{\inred{XX}}
      & \text{\inred{XX}}
      & \text{\inred{XX}}
      & \text{\inred{XX}}\\\hline
      \text{\# syntactic prod.}
      & \text{\inred{XXX}}
      & \text{\inred{XXX}}
      & \text{\inred{XXX}}
      & \text{\inred{XXX}}
      & \text{\inred{XXX}}
      & \text{\inred{XXX}}\\\hline
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r|r}
      \hline
      \textbf{old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{new version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c|}{\textbf{2020}}
      & \\\hline
      \Delta \; \text{\# lexical prod.}
      & \text{\inred{X}}
      & \text{\inred{X}}
      & \text{\inred{X}}
      & \text{\inred{X}}
      & \text{\inred{X}}\\\hline
      \Delta \; \text{\# syntactic prod.}
      & \text{\inred{XX}}
      & \text{\inred{XX}}
      & \text{\inred{XX}}
      & \text{\inred{XX}}
      & \text{\inred{XX}}\\\hline
    \end{array}
  \]
  \caption{The number of productions for lexical and
  syntactic grammars in ECMAScript specifications.}
  \label{fig:syntax-all-version}
\end{figure}

>>>>

\begin{figure}[t]
  \[
    \begin{array}{c|r|r|r|r|r?r}
      \hline
      \textbf{version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\hline
      \text{\# lexical prod.}
      & \text{78}
      & \text{78}
      & \text{78}
      & \text{81}
      & \text{81}
      & \text{79.2}\\\hline
      \text{\# syntactic prod.}
      & \text{157}
      & \text{167}
      & \text{167}
      & \text{174}
      & \text{175}
      & \text{168}\\\hline
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r?r}
      \hline
      \textbf{old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c?}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{new version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \\\hline
      \Delta \; \text{\# lexical prod.}
      & \text{3}
      & \text{5}
      & \text{6}
      & \text{0}
      & \text{4.7}\\\hline
      \Delta \; \text{\# syntactic prod.}
      & \text{140}
      & \text{15}
      & \text{8}
      & \text{2}
      & \text{55}\\\hline
    \end{array}
  \]
  \caption{The number of productions for lexical and
  syntactic grammars in ECMAScript specifications.}
  \label{fig:syntax-all-version}
\end{figure}
